---
title: "Linear Interpolation Example"
author: "Zarni Htet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(CDIPATools)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Linear Interpolation Concept

The linear interpolation equation to be used in the base function is below. The *y*<sub>0</sub> and *y*<sub>1</sub> would be either BMI or Media exposure variable. The *x*<sub>0</sub> and *x*<sub>1</sub> would be the time variable.

The *y* variable is the missing value we are looking for at time *x*. For BMI variable, the *x* corresponds to a time from Media exposure that is missing between the *x*<sub>0</sub> and the *x*<sub>1</sub> intervals. The inverse can be said of the Media Exposure variable to BMI as well.

Source: Linear Interpolation, Wikipedia


## 2-D Linear Interpolation

For 2-D Linear Interpolation, we have to provide 2 pairs of (x,y) coordinates and 1 coordinate point corresponding to the missing value. 

```{r}
missing.y <- LinInterpolate(3,5,1,3,2)
```
